---
title: "Assignment 1"
output: html_document
---
$~$
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(janitor)
library(modelr)
library(kableExtra)
```

####### *Loading Dataset*
```{r}
bcdata = read_csv("bcdata_Assignment1.csv") %>% 
  clean_names()
```
$~$

# Question 1
### Constructing Table Providing Summaries 
```{r, warning = FALSE}
bcdata %>% 
  select(!classification) %>% 
  map_df(.f = ~ broom::tidy(summary(.x)), .id = "Variable") %>% 
  select(Variable, mean, median, minimum, maximum) %>% 
  kbl(digits = 3,caption = "Summaries of Quantitative Features") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```
$~$

# Question 2 
### Recoding BMI into WHO-defined categories
```{r}
bcdata = bcdata %>% 
  mutate(bmi_who = as.factor(
    ifelse(bmi < 16.5, "severely underweight",
    ifelse(bmi < 18.5, "underweight",
    ifelse(bmi >= 18.5 & bmi < 24.9, "normal weight",
    ifelse(bmi >= 25 & bmi < 29.9, "overweight",
    ifelse(bmi >= 30 & bmi < 34.9, "obesity class I",
    ifelse(bmi >= 35 & bmi < 39.9, "obesity class II",
    ifelse (bmi >=40, "obesity class II", "N/A")))))))))

bcdata %>% 
  select(bmi, bmi_who)
```
$~$

# Question 3
### Bar Chart Shwoing Proportion of Breast Cancer Cases and Controls Within Each BMI Category
```{r}
bcdata %>% 
  group_by(bmi_who) %>% 
  ggplot(aes(x = fct_relevel(bmi_who, "severely underweight", "underweight", "normal weight", "overweight", "obesity class I", "obesity class II", "obesity class III"),
             y = prop.table(stat(count)), 
             fill = factor(classification),
             label = scales::percent(prop.table(stat(count))))) +
  geom_bar(position = position_dodge2(width = 0.9)) +
  geom_text(stat = 'count', position = position_dodge(0.9), vjust = -0.5, size = 3)+
  scale_y_continuous(labels = scales::percent) +
  scale_fill_discrete(labels = c("Healthy Controls", "Breast Cancer Patients")) +
  labs(title = "Breast Cancer Cases and Controls Within Each BMI Category",
       x = "BMI (WHO-defined Categories)",
       y = "Percentage",
       fill = "Classification")
```
$~$

# Question 4
### Logistic Regression Using Breast Cancer Classification as Outcome and Glucose, HOMA-IR, Leptin, BMI (continuous), and Age as Independent Variables
```{r}
bcdata = bcdata %>% 
  mutate(
    classification = recode(classification, '1' = '0', '2' = '1', .default = NA_character_),
    classification = as.numeric(classification))

logmodel = bcdata %>% 
  glm(classification ~ glucose + homa + leptin + bmi + age, data = ., family = binomial()) %>% 
  tidy() %>% 
  filter(term == "homa") %>% 
  select(term, estimate, std.error) %>%
  mutate(
    conf_low = exp(estimate - 1.96*std.error),
    conf_high = exp(estimate + 1.96*std.error)) %>% 
  select(-std.error)
  
logmodel %>% 
  kbl(digits = 3, caption = "Beta Estimate and 95% Confidence Interval Associated with 1-unit Change in HOMA-IR") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```
$~$

# Question 5
### Linear Regression Model Using Insulin as Outcome and BMI (continuous), Age, and Glucose as Independent Variables
```{r}
linmodel = lm(insulin ~ bmi + age + glucose, data = bcdata) %>% 
  tidy() %>% 
  filter(term == "age") %>% 
  select(term, estimate, std.error) %>%
  mutate(
    conf_low = exp(estimate - 1.96*std.error),
    conf_high = exp(estimate + 1.96*std.error)) %>% 
  select(-std.error)

linmodel %>% 
  kbl(digits = 3, caption = "Beta Estimate and 95% Confidence Interval Associated with 1-unit Change in Age") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```


